---
title: 'M√≥dulo :  Reproducible Resource'
author: "Geraldo Barbosa do Amarante"
date: 'Semana 02 - [Emiss√£o :   26 de novembro de 2017]'
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quest„o - 01
## LOADING AND PROCESSING THE DATA  
1.1 - Load the data.

1.2 - Process/transform the data (if necessary) into a format suitable for your analysis

```{r CODIGO01, echo=TRUE}
setwd("D:/coursera/ReproducibleResource/Semana02/ArquivodeDados")
library(readr)
atividade <- read_csv("./activity.csv")
atividadesemNA <- atividade[ with (atividade, { !(is.na(steps)) } ), ]
head(atividadesemNA)

```

## Quest„o - 02
## WHAT IS MEAN TOTALNUMBER OF STEPS TAKEN PER DAY
2.1 - Calculate the total number of steps taken per day

2.2 - If you do not understand the difference between a histogram and a barplot,
      research the difference between them. Make a histogram of the total number of steps taken each day

2.3 - Calculate and report the mean and median of the total number of steps taken per day

```{r CODIGO02, echo=TRUE}
library(dplyr)
agrupamentopordata <- group_by(atividadesemNA, date)
passosdiarios <- summarise(agrupamentopordata, total = sum(steps))
head(agrupamentopordata)
head(passosdiarios)
hist(passosdiarios$total, main="Histogram of total number of steps per day", 
     xlab="Total number of steps in a day",col = "yellow")
summary(passosdiarios)
```

## Quest„o - 03
## WHAT IS THE AVERAGE DAILY ACTIVITY PATTERN?
3.1 - Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number 
      of steps taken, averaged across all days (y-axis)
      
3.2 - Which 5-minute interval, on average across all the days in the dataset, contains the maximum number 
      of steps?

```{r CODIGO03, echo=TRUE}
passosporintervalo <- aggregate(steps ~ interval, atividadesemNA, mean)
plot(passosporintervalo$interval, passosporintervalo$steps, type='l', 
     main="THE AVERAGE DAILY ACTIVITY PATTERN", xlab="5-minute interval", 
     ylab="Averaged across all days",col="green")
valoresmaximos <- which.max(passosporintervalo$steps)
passosporintervalo[valoresmaximos, ]
```
## Quest„o - 04
## IMPUTING MISSING VALUES
4.1 - Calculate and report the total number of missing values in the dataset (i.e. the total number of 
       rows with NAs)

4.2 - Devise a strategy for filling in all of the missing values in the dataset. The strategy does not 
      need to be sophisticated. For example, you could use the mean/median for that day, or the mean for
      that 5-minute interval, etc.

4.3 - Create a new dataset that is equal to the original dataset but with the missing data filled in.

4.4 - Make a histogram of the total number of steps taken each day and Calculate and report the mean and 
      median total number of steps taken per day. Do these values differ from the estimates from the first
      part of the assignment? What is the impact of imputing missing data on the estimates of the total 
     daily number of steps?

```{r CODIGO04, echo=TRUE}
somaatividade <- sum(is.na(atividade))
for (i in 1:nrow(atividade)){
  if (is.na(atividade$steps[i])){
    valorintervalo <- atividade$interval[i]
    registro <- which(passosporintervalo$interval == valorintervalo)
    valorpasso <- passosporintervalo$steps[registro]
    atividade$steps[i] <- valorpasso
  }
}
somaatividade
valorintervalo
registro
valorpasso
atividadeagregada <- aggregate(steps ~ date, atividade, sum)
atividadeagregadasemNA <- aggregate(steps ~ date, atividadesemNA, sum)
hist(atividadeagregada$steps,main="Total number of steps per day", 
     xlab="Total steps in a day", col = "blue")
mean(atividadeagregada$steps)
```

## Quest„o - 05
## ARE THERE DIFFERENCES IN ACTIVITY PATTERNS BETWEEN WEEKDAYS AND WEEKENDS ?
5.1 - Create a new factor variable in the dataset with two levels - "weekday" and "weekend" 
      indicating whether a given date is a weekday or weekend day.

5.2 - Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval
      (x-axis) and the average number of steps taken, averaged across all weekday days or weekend
      days (y-axis). See the README file in the GitHub repository to see an example of what this 
      plot should look like using simulated data.
```{r CODIGO05, echo=TRUE}
library(ggplot2)
atividade['type_of_day'] <- weekdays(as.Date(atividade$date))
atividade$type_of_day[atividade$type_of_day  %in% c('Saturday','Sunday') ] <- "weekend"
atividade$type_of_day[atividade$type_of_day != "weekend"] <- "weekday"
atividade$type_of_day <- as.factor(atividade$type_of_day)
passosporintervalo <- aggregate(steps ~ interval + type_of_day, atividade, mean)
qplot(interval, 
      steps, 
      data = passosporintervalo, 
      geom=c("line"),
      xlab = "Interval", 
      ylab = "Number of steps", 
      main = "") +
  facet_wrap(~ type_of_day, ncol = 1)
```

## Brasil